R Notebook

### 2022-04-19 R/HumanDeaminationAnalysis.rmd

>>>>

```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))

plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "6-4 C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "6-4 C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))
```

# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
#                          title = "CPD C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
#                          title = "CPD C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# 
# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# ```

# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, STDEV,
#                          title = "CPD C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, STDEV,
#                          title = "CPD C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# 
# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, STDEV,
#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
#                          xAxisBreaks = c(23:31))
# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, STDEV,
#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
#                          xAxisBreaks = c(23:31))
# ```
